\section{Different encodings}\label{encodings}

    This section describes three
    ways of encoding conditional
    equations in QuickSpec. It is
    worth noting that these methods
    are general and could be used outside
    the context of QuickSpec. The
    idea of encoding conditionals
    as types is something users of
    QuickCheck\cite{Claessen2000}
    are familiar with\footnote{The QuickCheck distribution
    on hackage, \texttt{https://hackage.haskell.org/package/QuickCheck}, includes for an instance an implementation
    of the \texttt{NonNegative} type.}. 
    This work presents two alternative methods
    to type encoding. First however, we present type encoding
    in more detail.

    \subsection{Type encoding}\label{TE}

        Type encoding (abbreviated TE) is the idea of encoding
        predicates as a type with an invariant.
        More specifically
        it is saying that for a given predicate
        \begin{verbatim}
        p :: A -> B -> ... -> X -> Bool
        \end{verbatim}
        a type can be constructed
        \begin{verbatim}
        data Predicate_p = Predicate_p {a :: A, b :: B, ..., x :: X}
        \end{verbatim}
        such that 
        \begin{verbatim}
        t :: Predicate_p
        p (a t) (b t) ... (x t) = True
        \end{verbatim}
        As QuickSpec uses QuickCheck, which lets us define
        custom generators for random data, we can write a generator for 
        the predicate type which generates random instances that obey the invariant.
        An example of a predicate type is the one that encodes \texttt{Int}'s greater than zero
        \begin{verbatim}
        newtype PredicateType = PredicateType {x :: Int}

        instance Arbitrary PredicateType where
            arbtrary = fmap ((1+) . abs) arbitrary
        \end{verbatim}
        The equations involving predicate types are on the form
        \begin{verbatim}
        p :: PredicateType

        abs (x p) = x p

        \end{verbatim}
        which translates to $x > 0 \implies abs(x) = x$.

        In this encoding we need to be explicit about things such as conjunction
        of multiple predicates or predicates like $P\circ f$.
        Being explicit about these things introduces more overhead, therefore
        we want to find a light weight encoding scheme. Motivated by this
        we introduce function encoding.

        As we are looking for a general method for encoding predicates we need
        a way to automatically generate the instances of the \texttt{Arbitrary} type class.
        The naive way of doing this is to use the
        \texttt{suchThat}\footnote{\texttt{https://hackage.haskell.org/package/QuickCheck-2.8.2/docs/Test-QuickCheck-Gen.html}} 
        combinator. 

    \subsection{Function encoding}

        Function encoding (abbreviated FE) is the idea of encoding 
        predicates with functions. The idea is best
        illustrated with an example
        \begin{verbatim}
        -- p is a predicate
        p :: (a, b, c, ... , x) -> Bool

        -- default is a value such that
        p default = True

        -- The predicate is encoded as
        when_p :: (a, b, c, ... , x) -> (a, b, c, ... , x)
        when_p input
            | p input   = input
            | otherwise = data default
        \end{verbatim}
        In function encoding, an equation like
        \begin{verbatim}
        when_pos :: Int -> Int
        when_pos x
            | x > 0 = x
            | otherwise = 1

        abs (when_pos x) == when_pos x

        \end{verbatim}
        would be equivalent to the aformentioned $x > 0 \implies abs(x) = x$.
        Some care needs to be taken when choosing the default value.
        With combined encoding we do not need to make that decision ourselves.

%     \subsection{Combined encoding}\label{combined_encoding}
%        
%        Combined encoding is the idea that we can let the
%        default value of a function encoded predicate be a type
%        encoding of the predicate. A combined encoding can be illustrated
%        like this
%        \begin{verbatim}
%        -- p is a predicate
%        p :: (a, b, c, ..., x) -> Bool  
%
%        -- when_p is a combined encoding of p
%        when_p :: Predicate_p -> (a, b, c, ... , x) -> (a, b, c, ... , x)
%        when_p default input
%            | p input   = input
%            | otherwise = default
%        \end{verbatim}
%        The encoding of $x > 0 \implies abs(x) = x$ in combined encoding would look like
%        this
%        \begin{verbatim}
%        abs (when_pos p x) = when_pos p x
%        \end{verbatim}
